Vulnerability Analysis of Container Images in Neuroimaging

### 2020-04-21 paper.tex
changed citations

%%%% Packages %%%%
\usepackage{siunitx}
\usepackage{algpseudocode} % Algorithmic environment
\usepackage{xspace}
\usepackage{csvsimple}
\usepackage{minted} % Used for JSON highlighting
\usepackage{datatool}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{caption}
\usepackage[justification=centering]{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{verbatim}
\usepackage{adjustbox}
\usepackage{makecell}
\usepackage[flushleft]{threeparttable}

@@

This study involves three image scanning experiments.
The first experiment scans the images as is to report the existing vulnerabilities
inside the images. The scan report of
these images shows a large number of existing vulnerabilities which may pose
a potential security risk. These vulnerabilities exist due to the outdated
packages that are present inside images. So, the next step is to
take the necessary steps to improve security in the images. Therefore, there exist
two possible solutions.
The first one involves updating
all these images and then rescanning them, which constitutes the next experiment of our study. The second one
involves shrinking the size of the image
meaning that removing all unnecessary packages from the image to see the effect on the number of
vulnerabilities present inside the image, which will be presented as our third experiment.

@@

Docker uses a client-server architecture, where client containers communicate to
the server Docker Daemon also known as Docker engine.
Docker Daemon is a long-running process that manages all Docker images, containers, storage volumes, and networks.

@@

\subsubsection{Scanning tools used}

@@

In our experiments, we used a Docker image (\href{https://hub.docker.com/r/vanessa/stools-clair}{vanessa/stools-clair:v3.2.1})
for scanning and followed the steps mentioned in (\href{https://github.com/singularityhub/stools}{Stools Github})

@@

If there exist vulnerabilities in the container image, then we can
run after updating the
image. Updating the image involves updating all software packages that are
inside that image. We used a bash script (\href{https://github.com/kaurbhupinder/Vulnerability-Analysis}{Github}) 
to update all images, which checks the
package manager present inside the image and then according to that it
updates the image. However, this option affects the reproducibility
of the image, which means that the image cannot be used to verify the research
findings of other scientists.

\subsection{Image size Reduction process}

If we want to reduce number of vulnerabilities without effecting the reproducibility of the image,
image size reduction process is a good choice. In this process we reduce the number of packages
installed in the image by deleting unnecessary packages. For that to happen, we need to first figure
out which packages we need for the pipeline to fucntion properly. Here, we use Reprozip
\href{https://github.com/VIDA-NYU/reprozip}{https://github.com/VIDA-NYU/reprozip}. It is a tool that
is used to make applications reproducible~\cite{ChirigatiRSF16}. It traces operating system calls used by the
application while execution and then based on that it recognizes binaries, files, environment variables,
and library dependencies that will be used by the application for future reexecution. If the OS is
Debian or RPM based, Reprozip also
uses available package manager to acquire a list of distribution packages from where these files come from.
So, we got this list of packages from Reprozip that are needed for the application execution. 
After that, we expanded this list by adding important and required packages that are essential
for the system to function and finally figured out all the dependencies of these packages using debtree
(\href{http://manpages.ubuntu.com/manpages/xenial/man1/debtree.1.html}{http://manpages.ubuntu.com/manpages/xenial/man1/debtree.1.html}).
Ultimately, we kept these packages and removed remaining unnecessary packages. We used bash script

@@

When we add all regions of Venn diagram
we get total 20050 vulnerabilities in Bids and Boutiques images.
It is interesting to note that out of these vulnerabilities, 4453 vulnerabilities are only
reported by Anchore, 673 only reported by Clair, and 325 only detected by Vuls.

The number and type of vulnerabilities reported by the three scanners are drastically different from each other.
The question arises why these scanners report different numbers and types of vulnerabilities.
How their logic differs and what exactly is making these results different than each other.

According to our investigation of these results, below are some of the reasons for
getting different results from these scanners. These reasons include bugs in scanners,
some scanners ignoring vulnerabilities in a particular package, referring to different databases,
how frequently they are updating their databases, etc.

@@

When the images are rescanned after the update, results changed drastically. However, there are still
vulnerabilities reported by these scanners but there are no fixes available for these vulnerabilities
to date.
\begin{comment}
There are only two
options, either you accept those vulnerabilities and use that image, or you discard that image.
So one thing is clear here that even if we keep our images up to date there will be still some
vulnerabilities that we have to face.
\end{comment}
Figure~\ref{fig:graph2} compares the number of vulnerabilities that are detected by Anchore before and after 
the update of these images.
After the update, the vulnerabilities mostly have \textit{Low, Negligible or Medium} severity status.
Also, after the update, the number of vulnerabilities have a mild slope meaning that there
are a fixed set of packages that contain vulnerabilities and have no fix yet.
\begin{figure*}[!htb]
        {\includegraphics[width=\textwidth]
        {Figures/afterupdatewithpackage.pdf}}
        \caption{\label{fig:graph2} Scatterplot representing the number of vulnerabilities before and 
	after update of the images}
      \end{figure*}
\subsection{Effect Of Size Reduction}

Our last experiment shows deleting unnecessary packages from the image also helps to reduce
the number of vulnerabilities by significant number.
\bibliography{bibliography}

>>>>

%%%% Packages %%%%
\usepackage{siunitx}
\usepackage{algpseudocode} % Algorithmic environment
\usepackage{xspace}
\usepackage{csvsimple}
\usepackage{minted} % Used for JSON highlighting
\usepackage{datatool}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{caption}
\usepackage[justification=centering]{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{verbatim}
\usepackage{adjustbox}
\usepackage{makecell}
\usepackage{titlesec}
\usepackage[flushleft]{threeparttable}

@@

This study involves three image scanning experiments.
The first experiment scans the images as is to report the existing vulnerabilities
inside the images. The scan report of
these images shows a large number of existing vulnerabilities which may pose
a potential security risk. These vulnerabilities exist due to the outdated
packages that are present inside the images. So, the next step is to
take the necessary steps to improve security in the images. Therefore, there exist
two possible solutions.
The first one involves updating
all these images and then rescanning them, which constitutes the second experiment of our study. The next 
experiment involves shrinking the size of the image
meaning that removing all unnecessary packages from the image to see the effect on the number of
vulnerabilities present inside the image, which will be presented as our third experiment.

@@

Docker uses a client-server architecture, where client, containers, communicate to
the server, Docker Daemon, which is also known as Docker engine.
Docker Daemon is a long-running process that manages all Docker images, containers, storage volumes, and networks.

@@

%\subsubsection{Scanning tools used}

@@

In our experiments, we used a Docker image (\href{https://hub.docker.com/r/vanessa/stools-clair}{vanessa/stools-clair:v3.2.1})
for scanning and followed the steps mentioned in \href{https://github.com/singularityhub/stools}{Stools Github}.

@@

If there exist vulnerabilities in the container image, then we can
run after updating the
image. Updating the image involves updating all software packages that are
inside that image. We used a bash script (\href{https://github.com/kaurbhupinder/Vulnerability-Analysis}{Github}) 
to update all images, which checks the
package manager present inside the image and then according to that it
updates the image. However, this option affects the reproducibility
of the image, which means that the image cannot be used to verify the research
findings of other scientists.
\linespread{0.5}
\subsection{Image size Reduction process}

If we want to reduce number of vulnerabilities without effecting the reproducibility of the image,
image size reduction process is a good choice. In this process we reduce the number of packages
installed in the image by deleting unnecessary packages. For that to happen, we need to first figure
out which packages we need for the pipeline to fucntion properly. Here, we used 
Reprozip~\cite{rampin2016reprozip}. It is a tool that
is used to make applications reproducible. It traces operating system calls used by the
application while execution and then based on that it recognizes binaries, files, environment variables,
and library dependencies that will be used by the application for future reexecution. If the OS is
Debian or RPM based, Reprozip also
uses available package manager to acquire a list of distribution packages from where these files come from.
So, we got a list of packages from Reprozip that are needed for the application execution. 
After that, we expanded this list by adding important and required packages that are essential
for the system to function and finally figured out all the dependencies of these packages using Debtree
~\cite{debtree}.
Ultimately, we kept these packages and removed remaining unnecessary packages. We used a bash script
(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/script.sh}{Github}) for getting
a list of unnecessary packages.

@@

When we add all regions of Venn diagram
we get total 20050 vulnerabilities in BIDS apps and Boutiques images.
It is interesting to note that out of these vulnerabilities, 4453 vulnerabilities are only
reported by Anchore, 673 reported only by Clair, and 325 detected only by Vuls.

The number and type of vulnerabilities reported by the three scanners are drastically different from each other.
It was interesting to investigate the reasons of these differences.
%these scanners report different numbers and types of vulnerabilities.
%How their logic differs and what exactly is making these results different than each other.

According to our investigation of these results, below are some of the reasons for
getting different results from these scanners. These reasons include bugs in scanners,
some scanners ignoring vulnerabilities in a Linux-Kernel header packages, referring to different databases,
how frequently they are updating their databases, etc.

@@

When the images are rescanned after the update, results changed drastically. However, there are still
vulnerabilities reported by these scanners but there are no fixes available for these vulnerabilities
to date.
\begin{comment}
There are only two
options, either you accept those vulnerabilities and use that image, or you discard that image.
So one thing is clear here that even if we keep our images up to date there will be still some
vulnerabilities that we have to face.
\end{comment}
Figure~\ref{fig:graph2} represents the number of vulnerabilities that are detected by Anchore before and after 
the update of these images.
After the update, the vulnerabilities mostly have \textit{Low, Negligible or Medium} severity status.
Also, after the update, the number of vulnerabilities have a mild slope meaning that there
are a fixed set of packages that contain vulnerabilities and have no fix yet.
\begin{figure*}[!htb]
        {\includegraphics[width=\textwidth]
        {Figures/afterupdatewithpackage.pdf}}
        \caption{\label{fig:graph2} Scatterplot representing the number of vulnerabilities before and 
	after update of the images}
      \end{figure*}
\subsection{Effect Of Size Reduction}

Our last experiment shows deleting unnecessary packages from the image also helps to reduce
the number of vulnerabilities by a significant number. We started this experiment with
\textit{bids/example} image and deleted 61 unnecessary packages out of total 528 packages, which helped
to reduce 838 vulnerabilities to 523. Later, we also checked with \textit{bids/freesurfer} image, which allowed
to delete 71 unnecessary packages out of total 298 packages. Consequently, reducing number of vulnerabilities
from 353 to 101.
\bibliography{bibliography}
